Simulation of Congenital Heart Defect Corrective Surgeries Using Thin Shell Elements

### 2012-03-02 Doc/Miccai/abstract.tex
changes to abstract
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@391 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

Pediatric cardiac surgery is particularly challenging because the final decisions on the procedure choice take place at the last minute.
The work presented in this paper aims at proposing an interactive software dedicated to preoperative planning.
This new tool would permit to evaluate several possible surgery on a virtual anatomy of the patient and anticipate the decisions.
As the surgery involves a reconfiguration of the blood vessels that are close to the heart.
During the surgery, the vessel walls are deformed, cut, and reconnected to other vessels.
We propose to anticipate the geometry changes of the vessel walls using a simulation based on thin-shell elements.
We demonstrate that our approach allows for simulating the results of low-level surgical procedures, with a unified strategy for joining the vessel models and simulate their subsequent behavior.

>>>>

Pediatric cardiac surgery is particularly challenging because the final decisions on the procedure choice take place at the last minute.
The work presented in this paper aims at proposing an interactive software dedicated to preoperative planning.
This new tool would permit to evaluate several possible surgical procedures on a virtual anatomy of the patient and anticipate the decisions.
The surgery involves a reconfiguration of the blood vessels that are close to the heart.
During the surgery, the vessel walls are deformed, cut, and reconnected to other vessels or closed with an artificial patch.
We propose to anticipate the geometry changes of the vessel walls using a simulation based on thin-shell elements.
We demonstrate that our approach allows for simulating the results of low-level surgical procedures, with a unified strategy for joining the vessel models and simulate their subsequent behavior.
